Comparison of FDR methods on GWAS with SummarizedBenchmark

### 2017-12-14 datasets/GWAS/GWAS-SummarizedBenchmark.Rmd
First success at efficient LD pruning

```{r, GWAS1-diag, fig.width=10, fig.height=3.5}
strat_hist(bmi, pvalue="pval", covariate="ind_covar_N", maxy=3)
rank_scatter(bmi, pvalue="pval", covariate="ind_covar_N")
```

@@

```{r, GWAS1-diag2, fig.width=10, fig.height=3.5}
strat_hist(bmi, pvalue="pval", covariate="ind_covar_AF", maxy=3)
rank_scatter(bmi, pvalue="pval", covariate="ind_covar_AF")
```

@@

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
mcols(sb)$ind_covariate <- abs(mcols(sb)$ind_covar_AF-0.5)
plotCovariateBoxplots(sb, alpha=0.1, nsets=6, methods=methods, trans=log2, maxNum=5)

>>>>

```{r, GWAS1-diag, fig.width=10, fig.height=3.5}
strat_hist(bmi, pvalue="pval", covariate="ind_covar_N", maxy=2)
rank_scatter(bmi, pvalue="pval", covariate="ind_covar_N")
```

@@

```{r, GWAS1-diag2, fig.width=10, fig.height=3.5}
strat_hist(bmi, pvalue="pval", covariate="ind_covar_AF", maxy=2)
rank_scatter(bmi, pvalue="pval", covariate="ind_covar_AF")
```

@@

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
mcols(sb)$ind_covariate <- abs(mcols(sb)$ind_covar_AF-0.5)
plotCovariateBoxplots(sb, alpha=0.1, nsets=6, methods=methods, maxNum=5)
